---
title: "Lecture 5: EDA"
format: html
editor: visual
---

## Read Dataset #1

```{r, message = F}
library(tidyverse)
sharks <- read_csv("https://github.com/stat408/Lecture5/raw/master/shark_attacks.csv")
```


```{r}
glimpse(sharks)
```

Many of these variables will require additional expertise dealing with text strings, so we'll come back to this dataset later in class.


### Activity #1

Create a figure to show shark attacks by year



### Activity #2

Create a figure to show shark attacks in the five countries with the most attacks.



### Activity #3

Create a figure to show shark attacks by year in the five countries with the most attacks.



### Activity #4

Create a [waffle plot](https://r-charts.com/part-whole/waffle-chart-ggplot2/) to indicate common activity when a shark attack occurred.

```{r}
library(waffle)

```

## Read Dataset #2

```{r, message = F}
seattle_in <- read_csv('http://math.montana.edu/ahoegh/teaching/stat408/datasets/SeattleHousing.csv')
glimpse(seattle_in)
```

### Activity #5

Pose a question and create a visualization to explore that question.

